A Parallel Geometric Multigrid Algorithm

### 2013-08-01 htdocs/multigrid.tex
mgrid comments
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2096 40876441-3496-0410-a613-a2fca35b2ae2

>>>>

\section{Speculation}

The following remarks are relevant for the branch of the code living
in the \texttt{testcharge} directory, where we have SOR (both uniform
permitivity and heterogenous permitivity) and should shortly have a
Fourier solver (uniform permeativity) available.

\subsection{Coordinate system}

The existing code has a single coordinaite system which corresponds
to the fine grid $\Omega_h$ in the multipgrid picture. Details of the
coordinate system (global and local extent; MPI communicators; 3d-to-1d
indexing functions, etc) are encapsulated in \texttt{coords.c}.
\begin{enumerate}
\item
As a first step towards a multigrid implementation, it would be
desirable to ``objectify'' formally a \texttt{coods\_t} data type.
This would be explicitly referenced in all existing fine grid
contexts (and is desirable on other grounds as well).
\item
For multigrid, one could then instantiate one \texttt{coords\_t}
object for each level of the grid $\Omega_k$ to allow corresponding
grid operations at a given level.
\item
A second option would be to retain a single \texttt{coords\_t} object,
but add functionality to recognise a ggrid level $k$ and perform the
necessary arithmetic/logic assuning uniform refinement. (This is
probably a less elegant and flexible solution, if more compact.)
\end{enumerate}

\subsection{Grid data structure(s)}

Each level of the grid $\Omega_k$ requires coordinate information,
but also local storage for three-dimensional field quantities, eg.,
$f_k(x,y,z)$. Local field quantities are expected to require a halo
region of extent \texttt{nhalo} cf. existing field quantities on the
fine grid. This allows interpolation and restriction operators to be
evalautated locally.

So, a grid-level structure might contain
\begin{verbatim}
  struct grid_s {
    int k;               /* the grid level */
    coords_t * coords;   /* coordinate information this level */
    field_t * f;         /* rhs */
    ...
  }
\end{verbatim}
A multigrid structure would then contain an array of grids for levels
$k = 1, \ldots, k_{max}$, information replicated on all MPI tasks:
\begin{verbatim}
  struct mgrid_s {
    int kmax;         /* the number of levels */
    grid_t ** level;  /* array of grid objects */
    ...
  }
\end{verbatim}

\subsection{The limit of local cosrsening}

For a given uniform domain decomposition of the fine grid, local
restriction or coarsening can be carried out to the point where
there is a grid of extent one in the local domain. This limits
the extent of local coarsening. At this point, further coarsening
might be based on coarsening the processor grid in the same spirit
as the computational grid.

\subsection{Issues}

\begin{enumerate}
\item
Can we use e.g., PetSc to test some options/performance before starting to
code?
\item
Do we want to limit ourselves to regular system sizes (i.e., 2$^n$)
and processor decompositions?
\item
Can the approach be extended to a threaded model (e.g., GPU)?
\end{enumerate}
